---
title: "Activity Log of UNSIAP Data Visualization E-Learning Course"
author: "Christophe Bontemps and Jing Zhao"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document: default
  html_document:  
    code_folding: hide
    highlight: tango
    number_sections: yes
    theme: lumen
  html_notebook: default
---

```{r setup, include=FALSE}
# Code folding oprion needs echo = TRUE to work 

knitr::opts_chunk$set( message = FALSE, warning = FALSE, 
                       results =FALSE, echo = TRUE, 
                       dev="png", 
                       fig.align = 'center',
                       dev.args=list(type="cairo"), dpi=96)

# Some colors we may want to use
SIAP.color <- "#0385a8"


```


```{r libraries}
# get knit worked for Mac
library(Cairo)
library(tidyverse)
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)
library(plotly)
```

# Data Cleaning
```{r CourseParameters}
# Course parameters
CourseStartDate <-"2021-01-13"
FileDate <-  20210304 #20210217  #20210201     # 20210127

```




###  Event data set:  (*`r paste0("Data/logs_DTV20_", FileDate,".csv")`*){-}

```{r LogData}

data_log <- read.csv(paste0("Data/logs_DTV20_", FileDate,".csv"))

FileNameLog <- paste0("Data/logs_DTV20_", FileDate,".csv") 

# I have a strange pb with the name of the Time variable. fixing it quick and dirty mode !
data_log <- data_log %>% 
  rename(Time = ï..Time ) 

nrow(data_log)

```

The Moodle platform allows the recording of many evetns during a course. Several data sets can then be downloaded (.csv format) for an anlysis of the activity of the learners. In fact all the events are recorded, with a time stamp, in a single log file. One field gathers the detail of each event. This field can be parded and informations on the user, the activity and the event can be extracted.

For this course, we recorded **`r nrow(data_log)`** events of different nature, that have to be cleaned.   

```{r cleaning}
## Remove less relevant observations 
#remove administrators

data_log <- data_log[!(data_log$User.full.name=="Christophe Bontemps" | data_log$User.full.name=="Ni Ni Thein" | data_log$Component=="Recycle bin"),]
```




```{r RemoveEvents}
#remove less relevant events

r <- unique(data_log$Event.name)
# the events to remove

rem_events <- c("Tour ended", "Tour ended", "Group member added","Role assigned",
                "Course searched", "User list viewed", "User profile viewed",
                "Subscription created", 
                "User profile viewed", "User list viewed", "Course user report viewed",
                "Badge listing viewed", "User report viewed", "Course module instance list viewed",
                "Read tracking disabled", 
                "User enrolled in course", "Discussion deleted" , "Post deleted", 
                "Step shown", "Tour started", "Tour reset", "Quiz report viewed",
                "Subscription deleted", "User unenrolled from course", "Group member removed",
                "Role unassigned",  "Discussion subscription deleted", "Tag added to an item",
                "Grade deleted", tail(r, n=11))
# rem_events

# remove events
data_log <- data_log[!data_log$Event.name %in% rem_events, ]

```

###  Extract numbers(ID) and text from *Description* field {-}


```{r ExtractIDs}
# Extract course ID
CourseID <- str_match(data_log$Description, "(?i)\\bcourse with id '?\\s*(\\d+)")[,2]


# Extract Learners ID
LearnerID <- str_match(data_log$Description, "(?i)\\buser with id '?\\s*(\\d+)")[,2]

# Extract module ID
ModuleID <- str_match(data_log$Description, "(?i)\\bsection number '?\\s*(\\d+)")[,2]

# unique(ModuleID) # the actions applied on Modules that are hidden from students are from stuffs like Shimizu san, Eunkoo, and me. We are not removed before. 

#Extract activity ID
ActID <- str_match(data_log$Description, "(?i)\\bcourse module id '?\\s*(\\d+)")[,2]
# unique(ActID)

# Extract activity type. 
# Note:**Many students also accessed old version such as "OLD-Video".**
Act_type <- str_match(data_log$Event.context,  "(?<=\\[).+?(?=\\])")[,1]
# unique(Act_type)# Many students also accessed old version such as "OLD-Video".


```

# Cleaned log (*course_log*) 


```{r CourseLogData}
#CourseID is not added since it means this datavis course
course_log <- data.frame(data_log, ModuleID, LearnerID, ActID, Act_type)

NbLearner <- count(unique((course_log %>%
              filter(!is.na(Event.name) & !is.na(ModuleID)) %>%
              select(LearnerID))))

```

> The course started on **`r CourseStartDate`**. So, **`r paste0(NbLearner)`** different Learners visited the plateform and the course. 

###  Extractime time event from the data {-}

```{r TimeID}
# Main course data frame 
course_log <- course_log  %>%
           mutate(Date = str_split(course_log$Time, ", " , simplify = TRUE)[,1],
                  HoursMin = str_split(course_log$Time, ", " , simplify = TRUE)[,2])

course_log <- course_log  %>%
          mutate(HoursMin = format(strptime(course_log$HoursMin, "%H:%M"), format = "%H:%M"),
          Date = as.Date(course_log$Date, "%d/%m/%y"))%>%
          filter(Date >= CourseStartDate) # rm before the the course started (13 Jan)


# Create day time range
# extract the hour and create time range. 
t <- course_log %>%
  select(HoursMin) %>%
  extract(HoursMin, 'Time_range', regex = "([\\d.]+)[^\\d.]", remove = FALSE) %>%
  mutate(Time_range = as.numeric(Time_range))

# a loop for time range
  for (i in list(t$Time_range)) {
  i = paste0(formatC(i, format="d",flag="0",width=2),":00", "-", formatC(i+1, format="d",flag="0",width=2), ":00")
  course_log$Time_range <- i
}

# unique(course_log$Time_range)

course_log <- course_log %>%
  mutate(DayID = group_indices(., Date))%>%
  mutate(TimeID = as.numeric(str_extract(course_log$Time_range, "([\\d.]+)")), 
         DayOfWeek = lubridate::wday(Date), 
         IsSunday  = as.factor(DayOfWeek ==7)) 



```


## Events

```{r ActivityData}
# Same date as Log file 
progress <-read.csv(paste0("Data/progress.dtv20_",FileDate,".csv"), header = FALSE) 

# Extract the activity names in order (hence the Header = FALSE above!)
actname <- progress[1,]
actname <- actname[colSums(is.na(actname) | actname == "") != nrow(actname)]
actname <- as.data.frame(t(actname[,-(1:2)]))
names(actname)[1] <- "Actname2"
actname <- actname %>%
  mutate(ActOrder = row_number())

```


``````{r ModuleNb}
# Matching and adding columns
course_log <- course_log  %>%
  mutate(Actname = str_split(course_log$Event.context, ": ", simplify = TRUE)[,2])%>%
  left_join(actname, by = c("Actname" = "Actname2"))


## Add module ID by the name of activities
# TODO: Check the Modules ID associated with activities. 
# course_log %>% 
#   select(ActOrder, Actname) %>%
# unique()%>%
#   View()

### So Far 74 activities
course_log <- course_log %>%
            mutate(ModuleID_2 = case_when(ActOrder == 1 ~ 0,
                                          between(ActOrder, 1, 13) ~ 1,
                                          between(ActOrder, 14, 22) ~ 2,
                                          between(ActOrder, 23, 33) ~ 3,
                                          between(ActOrder, 34, 46) ~ 4,
                                          between(ActOrder, 47, 62) ~ 5,
                                          between(ActOrder, 63, 74) ~ 6,
                                            )) %>%
   mutate(ActOrder = formatC(ActOrder, format="d",flag="0",width=2)) %>%
  filter(ActOrder <=74 & ActOrder>0)

```

After cleaning and refining the data we have some useful information about the course. 

>   There are **`r length(unique(course_log$Actname))`**  different *activities* (resources) in the course and reported in this log. These activities can be regrouped in a typology of **`r length(unique(course_log$Event.name))-1`**  different type of events (as defined by Moodle)


### Type of Events {-}

```{r TypeEvents}
course_log %>%
  filter(!is.na(Event.name)) %>%
  mutate(SpecificEvent = ifelse(str_detect(Event.name, "Quiz"), "Quiz",
                                ifelse(str_detect(Event.name, "Discussion")|
                                         str_detect(Event.name, "Post"), "Forum","Other"))) %>%
  group_by(Event.name, SpecificEvent) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 25) %>% 
  ggplot()+
  aes(x=reorder(Event.name, Learners), y=Learners, fill= SpecificEvent)+
  geom_bar(stat='identity')+
  labs(x="Events", y="Number of Learners", 
       subtitle = paste("The course has", length(unique(course_log$Event.name))-1,"different events (Final date ",
                        as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Total number of learners per type of activity")+
  scale_fill_manual("Type of Event",values=c("orange", "grey", SIAP.color)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()

## Stat 
foo <-course_log %>%
  filter(
    str_detect(Event.name, "Quiz"))%>%
  mutate(
    Q = n_distinct(LearnerID) )

goo <-course_log %>%
  filter(
    str_detect(Event.name, "created"))%>%
  mutate(
    Q = n_distinct(LearnerID) )

hoo <-course_log %>%
  filter(
    str_detect(Event.context, "Forum"))%>%
  mutate(
    Q = n_distinct(ActID) )

```
This means that among the  **`r paste0(NbLearner)`** participants that visited the course, only  **`r max(foo$Q)`**  ( *`r round(100* max(foo$Q)/NbLearner, 1)`* %)   viewed or attempted a quiz at least once.  We can also note that **`r max(goo$Q)`**  ( *`r round(100* max(goo$Q)/NbLearner, 1)`* %)  participants posted at least one post in any of the **`r max(hoo$Q)`** forums proposed.   

```{r, eval = FALSE}
#Learners event counts (top and bottom Learners)
course_log %>%
  filter(!is.na(LearnerID)) %>%
  count(LearnerID) %>%
  mutate(rank = dense_rank(desc(n))) %>% 
  filter(row_number() >= max(row_number()) - 5 | rank <= 5) %>%
  ggplot()+
  aes(x=reorder(LearnerID, -n), y=n, 
      fill=factor(ifelse(rank <= 5,"Top 5","Bottom 5"))) +
  geom_bar(stat='identity') +
  labs(x="Learners' ID", y="Number of events", fill="",
       subtitle = paste(NbLearner,"Learners (Final Date ", as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Learners event counts (top and bottom Learners)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```


###  Events conducted by date and time of the day{-} 

We can observe the pattern of events over the whole period of the course with a clear decline of activity on Sundays, and some good response on Tuesdays, with the live lectures and webinars.  Tuesdays and wednesday seem to be the most active days.  The Chinese New Year has little direct but may have an indirect effet since the activity somehow explodes just after.       

```{r}

course_log %>%
  mutate(ParticularDays = ifelse(DayOfWeek ==7, "Sunday", 
                                 ifelse(DayOfWeek ==2 & DayID <45, "Webinar", "Regular"))  ) %>%
  filter(!is.na(LearnerID)) %>%
  ggplot()+
  #aes(x=fct_infreq(Date))+
  aes(x = as.factor(DayID),  fill = ParticularDays)+
  geom_bar(color = "white" )+
   annotate("rect", xmin = 28, xmax = 37,
                  ymin = 0, ymax = 4500,
                  fill = "orange" , alpha = .2)+
   annotate("text", x = 32, y = 4000,
          color= "orange",
          label = "Chinese \n New Year")+
  labs(x="Day since start", y="Number of events", 
       subtitle = paste("Nb of days", length(unique(course_log$Date)),"(Final date: ",
                        as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Number of events recorded on the platform by date")+
  hrbrthemes::scale_fill_ft() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))

```

- Active time by Learners

```{r}
course_log %>%
  filter(!is.na(Time_range)) %>%
  group_by(Time_range) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=reorder(Time_range, Time_range), y=Learners, 
      fill = ifelse(Learners> 100, "High", "Low"))+
  geom_bar(stat='identity')+
  labs(x="Time", y="Number of Learners", 
       subtitle = paste("JST (Final date ", as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Learners' Activity by Hour")+
  scale_fill_manual("Activity",values=c("orange", SIAP.color)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8), 
        axis.text.x = element_text(angle = 60))

#  coord_flip()
  
```


##  Modules and activities

### Activities accessed by number of Learners

> I changed the variable to have the lables and "see" which are the activities the most popular.  Could be good to the Module number too (1-6)!

```{r}
course_log %>%
  filter(!is.na(ActID)) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  mutate(rank = dense_rank(desc(Learners))) %>% 
  filter(rank <= 40) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(length(unique(ActID))-1,"activities (Final Date ", as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Activities accessed by number of Learners (top 30 activities)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```
### Time

- Active time by events

> (I reordered here to have a distribution over the day time but do not manage to rank the date corectly... 


## Suggestions
    
### Table of learners activities
Similar to the one I send but with selection of the final date; hat is thetable can be generated for any final date in the past. --> the idea is to do shiny app of that and change the date...

- Final date: `r as.Date(paste(FileDate), format = "%Y%m%d")` 

```{r BarActivities, fig.height=8, fig.width=10, out.width = "80%"}

final_date = as.Date(paste(FileDate), format = "%Y%m%d")

p <- course_log %>%
  filter(!is.na(ActID),
         Date <= final_date, 
         ModuleID_2 !=0) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID),
            ModuleID = as.factor(max(ModuleID_2))) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar( aes(fill = ModuleID),stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(course_log[c("ActID", "Date")]), Date==final_date)),"activities (Date ", final_date,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()

p
#ggplotly(p)

```






```{r}
final_date2 = as.Date(paste(FileDate), format = "%Y%m%d")

course_log %>%
  filter(!is.na(ActID),
         Date <= final_date2) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(course_log[c("ActID", "Date")]), Date==final_date2)),"activities (Date ", final_date2,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
```

 
 
 
### Heatmap of the activities: 

* Horizontally:  time since beginnig of course
* Vertically:  activities (first activity Module 1 on top, last activity of module 6 at the bottom)
* heat = Nb of views (nb of Learners or events) of each activity 

```{r}
course_log %>%
  filter(!is.na(ActOrder)) %>%
  mutate(ActOrder = formatC(ActOrder, format="d",flag="0",width=2))
```


- Sort by the ActOrder in ascending order    
```{r, fig.width=12, fig.height=19}
#Both Date and Date ID work. Date: the specific date since beginning; DayID: the first date = 1, and the second = 2, ...

course_log %>%
  filter(!is.na(ActOrder), 
         ModuleID_2 <= 6) %>%
  mutate(ActID.lab = paste(ActOrder,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y= ActID.lab, fill=Learners)+
  geom_tile()+
  scale_fill_gradient()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(FileDate),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)


```
- Sort by the frequency of activities 
```{r, fig.width=12,fig.height=18}
#Both Date and Date ID work. Date: the specific date since beginning; DayID: the first date = 1, and the second = 2, ...
course_log %>%
  filter(!is.na(ActID)) %>%
  mutate(ActID.lab = paste(ActID,"-",Event.context, "-")) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y=fct_rev(fct_infreq(ActID.lab)), fill=Learners)+
  geom_tile()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(FileDate),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)

```

```{r GradesFile}
Gdate <- 20210301
Grades.raw <- read.csv(paste0("Data/DTV20Grades-", Gdate,".csv"))

OldNames <- names(Grades.raw)[9:14]
NewNames  <- paste0("Test", seq(1,6,1))

Grades <- Grades.raw %>%
  rename_with(~NewNames[which(OldNames == .x)], .cols = OldNames) %>%
  mutate_at(vars(starts_with("Test")),funs(as.character)) %>%
  mutate_at(vars(starts_with("Test")),funs(as.numeric)) %>%
  select(First.name:Country, Email.address:Test6) %>%
  mutate(
    TotalTest = rowSums(dplyr::across(Test1:Test6), na.rm = T)
  ) 

## attempt to create a merging name
StudentsNames <- read.csv("Data/progress.dtv20_20210225.csv", header = TRUE)  %>%
  select(X, Email.address) %>%
  rename( User.full.name = X)

# We now have the full name in the grade file
Grades <- Grades %>%
  left_join(StudentsNames, by = c("Email.address"))
  


```


```{r ActivityTime}
# course_log <-  course_log %>%
#   group_by(User.full.name, Date, Actname) %>%
#   mutate( TimeperActivity = lubridate::as.duration(Time)) %>%
#   group_by(User.full.name, Date) %>%
#   mutate(TimeperDay = sum(TimeperActivity)) %>%
#   ungroup()
#  Still a problem in this computation since there may be hours btween two event...
```



```{r ActivityTime2}
learners_Time <-  course_log %>%
  select(User.full.name, LearnerID, , Actname, ActID, Event.name,Date, Time) %>%
  mutate(RealTime = lubridate::dmy_hm(Time)) %>%
  group_by(User.full.name, Date) %>%
  arrange(RealTime) %>%
  mutate(RawDiff = RealTime - lag(RealTime))  %>%
  filter(RawDiff < 3600)%>%
  group_by(User.full.name)%>%  
  summarize(TotalTime = sum(RawDiff, na.rm = TRUE), 
            NbAct = length(unique(ActID)), 
            NbDays = length(unique(Date))) %>%
  ungroup()
```


```{r LearnersFile}
learners <- learners_Time %>%
  left_join(Grades, by = "User.full.name") 


```

```{r}
learners %>%
 ggplot() +
 aes(x = NbAct, y = TotalTest, color = Country) +
 geom_jitter( width = 0.5, height = 0.5, alpha = 0.6) +
 facet_wrap(vars(Country)) +
 scale_color_hue() +
 theme_minimal()
```


```{r}

p <- learners %>%
 filter(!is.na(Country)) %>%
mutate(TotalTime = TotalTime/60) %>%
 ggplot() +
 aes(x = NbAct, y = TotalTest, colour = Country, toto = User.full.name) +
 geom_jitter(aes(size=as.numeric(TotalTime)), width = 0.5, height = 0.5, alpha = 0.6) +
# geom_vline (aes(xintercept =  median(TotalTime))) +
# facet_wrap(vars(Country)) +
 scale_color_hue() +
 theme_minimal()+
 theme(legend.position = "bottom")

p
#ggplotly(p)

```

