---
title: "Activity Log of UNSIAP Data Visualization E-Learning Course"
author: "Jing Zhao and Christophe Bontemps"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:  
    code_folding: hide
    highlight: tango
    number_sections: yes
    theme: lumen
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
# Code folding oprion needs echo = TRUE to work 

knitr::opts_chunk$set( message = FALSE, warning = FALSE, 
                       results =FALSE, echo = TRUE, 
                       dev="png", 
                       fig.align = 'center',
                       dev.args=list(type="cairo"), dpi=96)

# Some colors we may want to use
SIAP.color <- "#0385a8"


```


```{r libraries}
# get knit worked for Mac
library(Cairo)
library(tidyverse)
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)

```

# Import data &  Clean data
```{r CourseParameters}
# Course parameters

date <-  20210224 #20210217  #20210201     # 20210127

```

## Event data set:  (*`r paste0("Data/logs_DTV20_", date,".csv")`*)

```{r LogData}

data_log <- read.csv(paste0("Data/logs_DTV20_", date,".csv"))

file <- paste0("Data/logs_DTV20_", date,".csv") 


# I have a strange pb with the name of the Time variable. fixing it quick and dirty mode !
data_log$Time <- data_log$ï..Time #Time variable was removed when running this line


```

## Remove less relevant observations 
- remove administrators
```{r}
#remove administrator 
data_log <- data_log[!(data_log$User.full.name=="Christophe Bontemps" | data_log$User.full.name=="Ni Ni Thein" | data_log$Component=="Recycle bin"),]

```
- remove less relevant events (_all the listed events below are related to learners actions since the administrators actions have been removed above_)
```{r}
r <- unique(data_log$Event.name)
r
```


```{r RemoveEvents}
#remove less relevant events
# the events to remove
rem_events <- c("Tour ended", "Tour ended", "Group member added","Role assigned",
                "Course searched", "User list viewed", "User profile viewed",
                "Subscription created", 
                "User profile viewed", "User list viewed", "Course user report viewed",
                "Badge listing viewed", "User report viewed", "Course module instance list viewed",
                "Read tracking disabled", 
                "User enrolled in course", "Discussion deleted" , "Post deleted", 
                "Step shown", "Tour started", "Tour reset", "Quiz report viewed",
                "Subscription deleted", "User unenrolled from course", "Group member removed",
                "Role unassigned",  "Discussion subscription deleted", "Tag added to an item",
                "Grade deleted", tail(r, n=11))
rem_events

# remove events
data_log <- data_log[!data_log$Event.name %in% rem_events, ]

```

## Extract number and text from Description

- Extract course ID
```{r}
CourseID <- str_match(data_log$Description, "(?i)\\bcourse with id '?\\s*(\\d+)")[,2]
head(CourseID)
unique(CourseID)

```

- Extract Learners ID
```{r}
LearnerID <- str_match(data_log$Description, "(?i)\\buser with id '?\\s*(\\d+)")[,2]
head(LearnerID)
```

- Extract module ID
```{r}
ModuleID <- str_match(data_log$Description, "(?i)\\bsection number '?\\s*(\\d+)")[,2]
unique(ModuleID) # the actions applied on Modules that are hidden from students are from stuffs like Shimizu san, Eunkoo, and me. We are not removed before. 

```

- Extract activity ID
```{r}
ActID <- str_match(data_log$Description, "(?i)\\bcourse module id '?\\s*(\\d+)")[,2]
head(ActID)
unique(ActID)
```

- Extract activity type. Note:**Many students also accessed old version such as "OLD-Video".**
```{r}
Act_type <- str_match(data_log$Event.context,  "(?<=\\[).+?(?=\\])")[,1]
unique(Act_type)# Many students also accessed old version such as "OLD-Video".
```

 
- New dataframe with extracted ID
```{r}
#CourseID is not added since it means this datavis course
log_new <- data.frame(data_log, ModuleID, LearnerID, ActID, Act_type)

NbLearner <- count(unique((log_new %>%
              filter(!is.na(Event.name) & !is.na(ModuleID)) %>%
              select(LearnerID))))

```

## Fixing time data
- Split date and time
```{r}
log_new <- log_new  %>%
           mutate(Date = str_split(log_new$Time, ", " , simplify = TRUE)[,1],
                    Times = str_split(log_new$Time, ", " , simplify = TRUE)[,2])

```

- rm the date before the the course started (13 Jan), and format time and date
TODO: begining course data as parameter

```{r}
log_new <- log_new  %>%
          mutate(Times = format(strptime(log_new$Times, "%H:%M"), format = "%H:%M"))%>%
          mutate(Date = as.Date(log_new$Date, "%d/%m/%y"))%>%
          filter(Date >= "2021-01-13")
          
  
        
```

- Create day time range
```{r}
# extract the hour and create time range. 
t <- log_new %>%
  select(Times) %>%
  extract(Times, 'Time_range', regex = "([\\d.]+)[^\\d.]", remove = FALSE) %>%
  mutate(Time_range = as.numeric(Time_range))

# a loop for time range
  for (i in list(t$Time_range)) {
  i = paste0(formatC(i, format="d",flag="0",width=2),":00", "-", formatC(i+1, format="d",flag="0",width=2), ":00")
  log_new$Time_range <- i
}

unique(log_new$Time_range)
```
- Create date and time ID
```{r}
log_new <- log_new %>%
  mutate(DateID = group_indices(., Date))%>%
  mutate(TimeID = as.numeric(str_extract(log_new$Time_range, "([\\d.]+)")))

```

## Activity data set: Activity ID in order: ActOrder
TODO: Name and date of course's activities dataset (NOW: *progress.dtv20_20210225.csv*)  


```{r}
progress <- read.csv("Data/progress.dtv20_20210225.csv", header = FALSE)  # progress.dtv20_20210217.csv
# Extract the activity names in order
actname <- progress[1,]
actname <- actname[colSums(is.na(actname) | actname == "") != nrow(actname)]
actname <- as.data.frame(t(actname[,-(1:2)]))
names(actname)[1] <- "Actname2"
actname <- actname %>%
  mutate(ActOrder = row_number())

```

```{r}
# Matching and adding columns
log_new <- log_new  %>%
  mutate(Actname = str_split(log_new$Event.context, ": ", simplify = TRUE)[,2])%>%
  left_join(actname, by = c("Actname" = "Actname2"))
```

## Add module ID by the name of activities
TODO: Check the Modules ID associated with activities. 

```{r}
log_new <- log_new %>%
            mutate(ModuleID_2 = case_when(ActOrder == 1 ~ 0,
                                          between(ActOrder, 1, 13) ~ 1,
                                          between(ActOrder, 14, 22) ~ 2,
                                          between(ActOrder, 23, 33) ~ 3,
                                          between(ActOrder, 34, 46) ~ 4,
                                          between(ActOrder, 47, 62) ~ 5,
                                          between(ActOrder, 63, 76) ~ 6,
                                            )) %>%
   mutate(ActOrder = formatC(ActOrder, format="d",flag="0",width=2))
  

```



> So far, **`r paste0(NbLearner)`** different Learners visited the course.  There are **`r length(unique(log_new$Actname))`**  different activities that are reported in this log. Note that some activities are not available for learners. 


# Visualize some variables

### Events {-}
- Events conducted by number of Learners
```{r}
log_new %>%
  filter(!is.na(Event.name)) %>%
  group_by(Event.name) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 25) %>% 
  ggplot()+
  aes(x=reorder(Event.name, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Events", y="Number of Learners", 
       subtitle = paste(length(unique(log_new$Event.name))-1,"events (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Events conducted by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```
- Learners event counts (top and bottom Learners)
```{r}
log_new %>%
  filter(!is.na(LearnerID)) %>%
  count(LearnerID) %>%
  mutate(rank = dense_rank(desc(n))) %>% 
  filter(row_number() >= max(row_number()) - 5 | rank <= 5) %>%
  ggplot()+
  aes(x=reorder(LearnerID, -n), y=n, 
      fill=factor(ifelse(rank <= 5,"Top 5","Bottom 5")))+
      geom_bar(stat='identity')+
  labs(x="Learners' ID", y="Number of events", fill="",
       subtitle = paste(NbLearner,"Learners (Final Date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Learners event counts (top and bottom Learners)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```


###  Events conducted by date 

>CB : should start **after the course starts** officially and then follow the date order

```{r}
log_new %>%
  filter(!is.na(LearnerID)) %>%
  ggplot()+
  #aes(x=fct_infreq(Date))+
  aes(x = Date)+
  geom_bar()+
  labs(x="Date", y="Number of events", 
       subtitle = paste(length(unique(log_new$Date)),"days (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Number of events was conducted by date")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))
#  coord_flip()
```
##  Modules and activities

### Activities accessed by number of Learners

> I changed the variable to have the lables and "see" which are the activities the most popular.  Could be good to the Module number too (1-6)!

```{r}
log_new %>%
  filter(!is.na(ActID)) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  mutate(rank = dense_rank(desc(Learners))) %>% 
  filter(rank <= 40) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(length(unique(ActID))-1,"activities (Final Date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Activities accessed by number of Learners (top 30 activities)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```
### Time
- Active time by events

> (I reordered here to have a distribution over the day time but do not manage to rank the date corectly... 

- Active time by Learners

```{r}
log_new %>%
  filter(!is.na(Time_range)) %>%
  group_by(Time_range) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=reorder(Time_range, Time_range), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Time", y="Number of Learners", 
       subtitle = paste("JST (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Active time by Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8), 
        axis.text.x = element_text(angle = 60))

#  coord_flip()
  
```

## Suggestions
    
### Table of learners activities
Similar to the one I send but with selection of the final date; hat is thetable can be generated for any fianl date in the past. --> the idea is to do shiny app of that and change the date...

- Final date: `r as.Date(paste(date), format = "%Y%m%d")` 

```{r}

final_date = as.Date(paste(date), format = "%Y%m%d")

log_new %>%
  filter(!is.na(ActID),
         Date <= final_date) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(log_new[c("ActID", "Date")]), Date==final_date)),"activities (Date ", final_date,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  

```




- Final date: 20210131
```{r}
final_date2 = as.Date(paste(date), format = "%Y%m%d")

log_new %>%
  filter(!is.na(ActID),
         Date == final_date2) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(log_new[c("ActID", "Date")]), Date==final_date2)),"activities (Date ", final_date2,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
```

 
 
 
### Heatmap of the activities: 
    * Horizontally:  time since beginnig of course
    * Vertically:  activities (first activity Module 1 on top, last activity of module 6 at the bottom)
    * heat = Nb of views (nb of Learners or events) of each activity  
```{r}
log_new %>%
  filter(!is.na(ActOrder)) %>%
  mutate(ActOrder = formatC(ActOrder, format="d",flag="0",width=2))
```


- Sort by the ActOrder in ascending order    
```{r, fig.width=12,fig.height=12}
#Both Date and Date ID work. Date: the specific date since beginning; DateID: the first date = 1, and the second = 2, ...

log_new %>%
  filter(!is.na(ActOrder), 
         ModuleID_2 <= 6) %>%
  mutate(ActID.lab = paste(ActOrder,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y= ActID.lab, fill=Learners)+
  geom_tile()+
  scale_fill_gradient()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(date),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)


```
- Sort by the frequency of activities 
```{r, fig.width=12,fig.height=12}
#Both Date and Date ID work. Date: the specific date since beginning; DateID: the first date = 1, and the second = 2, ...
log_new %>%
  filter(!is.na(ActID)) %>%
  mutate(ActID.lab = paste(ActID,"-",Event.context, "-")) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y=fct_rev(fct_infreq(ActID.lab)), fill=Learners)+
  geom_tile()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(date),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)

```

