---
title: "Activity Log of UNSIAP Data Visualization E-Learning Course"
author: "Jing Zhao and Christophe Bontemps"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:  
    code_folding: hide
    highlight: tango
    number_sections: yes
    theme: lumen
  pdf_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
# Code folding oprion needs echo = TRUE to work 

knitr::opts_chunk$set( message = FALSE, warning = FALSE, 
                       results =FALSE, echo = TRUE, 
                       dev="png", 
                       fig.align = 'center',
                       dev.args=list(type="cairo"), dpi=96)

# Some colors we may want to use
SIAP.color <- "#0385a8"


```


```{r libraries}
# get knit worked for Mac
library(Cairo)
library(tidyverse)
library(stringr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(forcats)

```

# Import data &  Clean data

```{r data}

date <- 20210217  #20210201     # 20210127

data_log <- read.csv(paste0("Data/logs_DTV20_", date,".csv"))

file <- paste0("Data/logs_DTV20_", date,".csv") 


# I have a strange pb with the name of the Time variable. fixing it quick and dirty mode !
data_log$Time <- data_log$ï..Time #Time variable was removed when running this line


```

## Remove less relevant observations 
- remove administrators
```{r}
#remove administrator 
data_log <- data_log[!(data_log$User.full.name=="Christophe Bontemps" | data_log$User.full.name=="Ni Ni Thein" | data_log$Component=="Recycle bin"),]

```
- remove less relevant events (_all the listed events below are related to learners actions since the administrators actions have been removed above_)
```{r}
r <- unique(data_log$Event.name)
r
```
```{r}
#remove less relevant events
# the events to remove
rem_events <- c("Tour ended", "Tour ended", "Group member added","Role assigned", "Course searched", "User list viewed", "User profile viewed", "Subscription created", tail(r, n=11))
rem_events

# remove events
data_log <- data_log[!data_log$Event.name %in% rem_events, ]

```

## Extract number and text from Description

- Extract course ID
```{r}
CourseID <- str_match(data_log$Description, "(?i)\\bcourse with id '?\\s*(\\d+)")[,2]
head(CourseID)
unique(CourseID)
```

- Extract Learners ID
```{r}
LearnerID <- str_match(data_log$Description, "(?i)\\buser with id '?\\s*(\\d+)")[,2]
head(LearnerID)
```

- Extract module ID
```{r}
ModuleID <- str_match(data_log$Description, "(?i)\\bsection number '?\\s*(\\d+)")[,2]
unique(ModuleID) # the actions applied on Modules that are hidden from students are from stuffs like Shimizu san, Eunkoo, and me. We are not removed before. 

```

- Extract activity ID
```{r}
ActID <- str_match(data_log$Description, "(?i)\\bcourse module id '?\\s*(\\d+)")[,2]
head(ActID)
unique(ActID)
```

- Extract activity type. Note:**Many students also accessed old version such as "OLD-Video".**
```{r}
Act_type <- str_match(data_log$Event.context,  "(?<=\\[).+?(?=\\])")[,1]
unique(Act_type)# Many students also accessed old version such as "OLD-Video".
```

 
- New dataframe with extracted ID
```{r}
#CourseID is not added since it means this datavis course
log_new <- data.frame(data_log, ModuleID, LearnerID, ActID, Act_type)

NbLearner <- count(unique((log_new %>%
              filter(!is.na(Event.name) & !is.na(ModuleID)) %>%
              select(LearnerID))))

```


> **Note that there is no overlap of Activity ID and Module ID from Description**. E.g., We extracted the Module ID by "section number": "The user with id '11216' viewed the **section number '1'** of the course with id '97' and extracted the activity ID by "module number" as: "The user with id '10946' viewed the 'page' activity with **course module id '3250'**". The "section number" and "module number" do not exist at the same time in a sentence. _**Description is not perfect**_
```{r}
log_new %>%
  filter(!is.na(ActID),
         !is.na(ModuleID))
```


## Fixing time data
- Split date and time
```{r}
log_new <- log_new  %>%
           mutate(Date = str_split(log_new$Time, ", ", simplify = TRUE)[,1],
                    Times = str_split(log_new$Time, ", ", simplify = TRUE)[,2])

```

- rm the date before the the course started (13 Jan), and format time and date
```{r}
log_new <- log_new  %>%
          mutate(Times = format(strptime(log_new$Times, "%H:%M"), format = "%H:%M"))%>%
          mutate(Date = as.Date(log_new$Date, "%d/%m/%y"))%>%
          filter(Date >= "2021-01-13")
          
  
        
```

- Create time range
```{r}
# extract the hour and create time range. 
t <- log_new %>%
  select(Times) %>%
  extract(Times, 'Time_range', regex = "([\\d.]+)[^\\d.]", remove = FALSE) %>%
  mutate(Time_range = as.numeric(Time_range))

# a loop for time range
  for (i in list(t$Time_range)) {
  i = paste0(formatC(i, format="d",flag="0",width=2),":00", "-", formatC(i+1, format="d",flag="0",width=2), ":00")
  log_new$Time_range <- i
}

unique(log_new$Time_range)
```
- Create date and time ID
```{r}
log_new <- log_new %>%
  mutate(DateID = group_indices(., Date))%>%
  mutate(TimeID = as.numeric(str_extract(log_new$Time_range, "([\\d.]+)")))

```



> So far, **`r paste0(NbLearner)`** different Learners visited the course.  There are **`r length(unique(ModuleID))-1`**  different activities that are reported in this log. Note that some activities are not available for learners. 


# Visualize some variables

### Events {-}
- Events conducted by number of Learners
```{r}
log_new %>%
  filter(!is.na(Event.name)) %>%
  group_by(Event.name) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 25) %>% 
  ggplot()+
  aes(x=reorder(Event.name, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Events", y="Number of Learners", 
       subtitle = paste(length(unique(log_new$Event.name))-1,"events (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Events conducted by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```
- Learners event counts (top and bottom Learners)
```{r}
log_new %>%
  filter(!is.na(LearnerID)) %>%
  count(LearnerID) %>%
  mutate(rank = dense_rank(desc(n))) %>% 
  filter(row_number() >= max(row_number()) - 5 | rank <= 5) %>%
  ggplot()+
  aes(x=reorder(LearnerID, -n), y=n, 
      fill=factor(ifelse(rank <= 5,"Top 5","Bottom 5")))+
      geom_bar(stat='identity')+
  labs(x="Learners' ID", y="Number of events", fill="",
       subtitle = paste(NbLearner,"Learners (Final Date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Learners event counts (top and bottom Learners)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```
###  Events conducted by date 

>CB : should start **after the course starts** officially and then follow the date order

```{r}
log_new %>%
  filter(!is.na(LearnerID)) %>%
  ggplot()+
  #aes(x=fct_infreq(Date))+
  aes(x = Date)+
  geom_bar()+
  labs(x="Date", y="Number of events", 
       subtitle = paste(length(unique(log_new$Date)),"days (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Number of events was conducted by date")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))
#  coord_flip()
```
##  Modules and activities

### Activities accessed by number of Learners

> I changed the variable to have the lables and "see" which are the activities the most popular.  Could be good to the Module number too (1-6)!

```{r}
log_new %>%
  filter(!is.na(ActID)) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  mutate(rank = dense_rank(desc(Learners))) %>% 
  filter(rank <= 40) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(length(unique(ActID))-1,"activities (Final Date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Activities accessed by number of Learners (top 30 activities)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```
### Time
- Active time by events

> (I reordered here to have a distribution over the day time but do not manage to rank the date corectly... 

- Active time by Learners

```{r}
log_new %>%
  filter(!is.na(Time_range)) %>%
  group_by(Time_range) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=reorder(Time_range, Time_range), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Time", y="Number of Learners", 
       subtitle = paste("JST (Final date ", as.Date(as.character(date),format = "%Y%m%d"),")"))+
  ggtitle("Active time by Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8), 
        axis.text.x = element_text(angle = 60))

#  coord_flip()
  
```

## Suggestions
    
### Table of learners activities
Similar to the one I send but with selection of the final date; hat is thetable can be generated for any fianl date in the past. --> the idea is to do shiny app of that and change the date...

- Final date: `r as.Date(paste(date), format = "%Y%m%d")' 

```{r}

final_date = as.Date(paste(date), format = "%Y%m%d")

log_new %>%
  filter(!is.na(ActID),
         Date == final_date) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(log_new[c("ActID", "Date")]), Date==final_date)),"activities (Date ", final_date,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  

```




- Final data: 20210131
```{r}
final_date2 = as.Date(paste(date), format = "%Y%m%d")

log_new %>%
  filter(!is.na(ActID),
         Date == final_date2) %>%
  mutate( ActID.lab = paste(ActID,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(log_new[c("ActID", "Date")]), Date==final_date2)),"activities (Date ", final_date2,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
```

 
 
 
### Heatmap of the activities: 
    * Horizontally:  time since beginnig of course
    * Vertically:  activities (first activity Module 1 on top, last activity of module 6 at the bottom)
    * heat = Nb of views (nb of Learners or events) of each activity  

> Failed to generate the activities order from Module 1 to Module 6

- Sort by the ActID in ascending order    

```{r, fig.width=12,fig.height=12}
#Both Date and Date ID work. Date: the specific date since beginning; DateID: the first date = 1, and the second = 2, ...
#sort by the ActID in ascending order
log_new %>%
  filter(!is.na(ActID)) %>%
 # mutate(ActID.lab = paste(fct_rev(fct_inorder(ActID)),"-",Event.context)) %>%
  mutate(ActID.lab = paste(ActID,"-",Event.context, "-")) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y= ActID.lab, fill=Learners)+
  geom_tile()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(date),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)


```
- Sort by the frequency of activities 
```{r, fig.width=12,fig.height=12}
#Both Date and Date ID work. Date: the specific date since beginning; DateID: the first date = 1, and the second = 2, ...
log_new %>%
  filter(!is.na(ActID)) %>%
  mutate(ActID.lab = paste(ActID,"-",Event.context, "-")) %>%
  group_by(ActID.lab, Date) %>%
  summarize(Learners = n_distinct(LearnerID)) %>% 
  ggplot()+
  aes(x=Date, y=fct_rev(fct_infreq(ActID.lab)), fill=Learners)+
  geom_tile()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(date),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)

```

