---
title: "Feedback Report (F2F courses - Bespoke)"
subtitle: ""
author: "Christophe Bontemps"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    df_print: kable
    toc: yes
    keep_tex: yes
    fig_width: 6.5
    fig_height: 4
    extra_dependencies: float
  word_document:
    toc: no
  html_document:
    df_print: paged
    toc: yes
    toc_float: true
    keep_md: yes
    code_folding: show
    fig_width: 6.5
    fig_height: 4
always_allow_html: true
---


```{r Knitr_Global_Options, include=FALSE, cache=FALSE, echo=FALSE}
library(knitr)

# No code is shown here
knitr::opts_chunk$set(echo = FALSE)

# Other options used here 
opts_chunk$set(warning = FALSE, message = FALSE,
               fig.pos = "!H", fig.align = "center",
               autodep = TRUE, tidy = FALSE, cache = FALSE)

# In case of "weird" problem, uncomment the line below (cache issue)
# opts_chunk$set(cache.rebuild=TRUE) 

# My colors:
SIAP.color <- "#0385a8"
```

`r if(knitr:::pandoc_to() == "latex") {paste("\\large")}` 


```{r libraries}
# Analysis

library(tidyverse)
library(stringr)
# library(tidyr)
# library(forcats)
library(lubridate)

# Nice presentation of results
library(Cairo)
library(papeR)
library(xtable)
library(data.table)
library(kableExtra)
library(modelsummary)

# Graphics 

library(plotly)
library(wesanderson)
library(patchwork)
library(wordcloud)

#Text analysis
library(stringr)        
library(tm)

### using Tidytext
library(tidytext)  
library(textdata)

# Export
library(openxlsx)

```


```{r}
# Loading All the courses and their features 

 AllCourses <- read.csv("AllCoursesSIAP.csv")
```

```{r LoadedParameters}
# Loading course parameters. 
i.course <- 22

# Specific parameters
CourseName <- as.character(AllCourses[i.course, "Ref"])
CourseNameLong <- as.character(AllCourses[i.course, "Name"])
NbModules <- as.numeric(AllCourses[i.course, "NbMod"])
GradeMax <- as.numeric(AllCourses[i.course, "GradeMax"])
PercentThreshold <- as.numeric(AllCourses[i.course, "Threshold"])
WebinarDay <- as.numeric(AllCourses[i.course, "Webinar"])

# A bit tricky for the date...
CourseStartDate <- AllCourses %>% 
  slice(i.course) %>% 
  pull(Starts)
CourseEndDate <- AllCourses %>% 
  slice(i.course) %>% 
  pull(Ends)


# Additional parameters 
GradeThreshold <-GradeMax * (PercentThreshold/100)
```

\newpage

# ***`r CourseNameLong `***:  

## Data sets

```{r LoadData}
# Parse the data folder to find the latest files 

#### Feedback  File
# --> use Comma separated values

list.feedback<- list.files(path="Data/",pattern = glob2rx(paste0("Feedback*",CourseName,"*")),
                       full.names = TRUE,recursive = TRUE)
name_last_feedback <- list.feedback[which.max(file.mtime(list.feedback))]

# Normal take this one -->  Must be CSV!!
data.feedback <- read.csv(name_last_feedback, encoding = "utf-8")
```


```{r LoadDataDirect}
# Date of the last file found
FileDate <-as_date(file.mtime(name_last_feedback))

```


```{r}
# data.feedback <- data.feedback %>%
#   filter(!if_any(where(is.character), ~ str_detect(., "Xtophe")))    # remove My test evaluation

NbTotal <- nrow(data.feedback)
```


Our analysis uses the data collected on **`r format(FileDate, "%A %d %B")`** from the  *Feedback Form*^[File used is  *`r name_last_feedback`*]. A total of  **`r nrow(data.feedback)`** different learners provided **anonymously** their feedback and comments on the course.^[As of `r format(FileDate, "%A %d %B")`]


```{r NonUnicode}
# Data cleaning 
# remove comments written in Chinese (maybe not necessary since we imported in utf-8)
#data.feedback$Results  <- str_replace_all(data.feedback$Results, "[\u2E80-\u2FD5\u3190-\u319f\u3400-\u4DBF\u4E00-\u9FCC\uF900-\uFAAD]", "")

# data.feedback$Comments  <- str_replace_all(data.feedback$Comments, "[\u2E80-\u2FD5\u3190-\u319f\u3400-\u4DBF\u4E00-\u9FCC\uF900-\uFAAD]", "")


```


```{r TransformFactors}
# Transforming answers into factors
library(purrr)

# Define a function to harmonize the answers
harmonize_answers <- function(answer) {
  answer <- tolower(answer)
  if (grepl("strongly agree", answer)) {
    return("Strongly agree")
  } else if (grepl("somewhat agree", answer)) {
    return("Somewhat agree")
  } else if (grepl("strongly disagree", answer)) {
    return("Strongly disagree")
  } else if (grepl("disagree", answer)) {
    return("Disagree")
  } else if (grepl("agree", answer)) {
    return("Agree")
  } else {
    return(NA)
  }
}

# Define a function to convert a variable into a factor with 6 levels
factor_6_levels <- function(variable) {
  variable <- factor(variable, 
                     levels = c(
                       "Strongly disagree",
                       "Disagree",
                       "Somewhat disagree",
                       "Somewhat agree",
                       "Agree",
                       "Strongly agree"))
  return(variable)
}
```


```{r TransformFactors4}


# Define a function to harmonize the answers
harmonize_answers_4 <- function(answer) {
  answer <- tolower(answer)
  if (grepl("very useful", answer)) {
    return("Very useful")
  } else if (grepl("useful", answer)) {
    return("Useful")
  } else if (grepl("Somewhat useful", answer)) {
    return("Somewhat useful")
  } else if (grepl("not useful", answer)) {
    return("Not useful")
  } else {
    return(NA)
  }
}



factor_4_levels_Useful <- function(variable) {
  variable <- factor(variable, 
                     levels = c(
                       "Not useful",
                       "Somewhat useful",
                       "Useful",
                       "Very useful"))
  return(variable)
}


```

```{r NewGraphicFunction}
library(rlang)
response_plot_new <- function(data, idx, levels) {
  
  # ---- 1. Variable name from index ----
  xvar <- names(data)[idx]
  
  # ---- 2. Nice automatic title ----
  title <- gsub("\\.", " ", xvar)
  title <- stringr::str_squish(title)
  
 
  
  # Convert to ordered factor with 6 levels
  if (levels ==6){
     
    data[[xvar]] <- sapply(data[[xvar]], harmonize_answers)
    data[[xvar]] <- factor_6_levels(data[[xvar]])
  }
  else
  {
    data[[xvar]] <- sapply(data[[xvar]], harmonize_answers_4)
    data[[xvar]] <-factor_4_levels_Useful(data[[xvar]])
  }
  
  # ---- 4. Count including empty factor levels ----
  plotdata <- data %>%
    count(.data[[xvar]], drop = FALSE) %>%
    mutate(percent = n / sum(n) * 100)
  
  # Wrap the  title.
  title_clean <- str_wrap(title, width = 30)
  
  # ---- 5. Plot ----
  ggplot(plotdata, aes(x = .data[[xvar]], y = n)) +
    geom_col(fill = SIAP.color, alpha = 0.5) +
    geom_text(aes(label = paste0(round(percent, 1), "%")),
              hjust = 1.1, color = "white") +
    ggtitle(title_clean) +
    coord_flip() +
    labs(x = NULL)+
    scale_x_discrete(drop = FALSE) +  # <<< KEY LINE to have 6 levels
    scale_y_continuous(limits = c(0, NbTotal)) +
    theme_minimal() +
    theme(
      legend.position = "none",
      plot.title = element_text(size = 10)
    )
}

```

```{r SurveyNewFormat}
# Creating Graphics
## Relevance: (4 questions)

G_R1 <- response_plot_new(data.feedback, 7, 6)
G_R2 <- response_plot_new(data.feedback, 8,6)
G_R3 <- response_plot_new(data.feedback, 9,6)
G_R4 <- response_plot_new(data.feedback, 10,6)

## Sessions: (6 questions)

G_S1 <- response_plot_new(data.feedback, 11, 4)
G_S2 <- response_plot_new(data.feedback, 12, 4)
G_S3 <- response_plot_new(data.feedback, 13, 4)
G_S4 <- response_plot_new(data.feedback, 14, 4)
G_S5 <- response_plot_new(data.feedback, 15, 4)
G_S6 <- response_plot_new(data.feedback, 16, 4)

```

#  Evaluation of the different dimensions of the course

We asked the participants to value their experience on the course using a 6-level scale, on  different dimensions (*Knowledge, Usefulness, Quality*,...) 


- **Relevance**: (4 questions)
- **Session by Session**: 

## Relevance

```{r GraphicsRelev, fig.height=6}
all.R<- (G_R1 | G_R2) /(G_R3 | G_R4) 
all.R + 
  plot_annotation(title = 'About the course (Knowledge, Relevance, Quality) ',
                  caption = paste("Based on" , nrow(data.feedback)," responses (File date", FileDate,")"),
                  theme = theme(plot.title = element_text(size = 16))) 

```

## Sessions

We asked questions about the sessions

```{r GraphicsEff, fig.height=6}
all.S <- (G_S1 | G_S2) /(G_S3 | G_S4) /(G_S5 | G_S6) 
all.S + 
  plot_annotation(title = 'Session by Session answers',
                  caption = paste("Based on" , nrow(data.feedback)," responses (File date", FileDate,")"),
                  theme = theme(plot.title = element_text(size = 16))) 

```
\newpage

# Free text answers from particpants


```{r}
feedback_text <- function(data, idx) {
  
  # Extract column name
  colname <- names(data)[idx]
  
  # Extract the text column
  comments <- data[[idx]]
  
  # Convert to character to avoid factor issues
  comments <- as.character(comments)
  
  # Clean entries: remove empty, NA, and variations of "none"
  comments_clean <- comments %>%
    str_trim() %>%
    na_if("") %>%
    na_if("NA") %>%
    na_if("N/A") %>%
    na_if("n/a") %>%
    na_if("N/a") %>%
    na_if("None") %>%
    na_if("none") %>%
    na_if("NONe") %>%
    na_if("Non") %>%
    na_if("non") 
  
  # Remove NAs
  comments_clean <- comments_clean[!is.na(comments_clean)]
  
  # If nothing left, return an empty tibble with a message
  if (length(comments_clean) == 0) {
    return(tibble(Comment = "No valid feedback provided."))
  }
  
  # Extract raw column name
  raw_title <- names(data)[idx]
  
  # Clean title: remove dots and format nicely
  clean_title <- raw_title %>%
    str_replace_all("\\.", " ") %>%
    str_to_sentence()      # or str_to_title()
  
  
  # Create a clean table with wrapped text
  tbl <- tibble(
    title = clean_title,
    Comment = str_wrap(comments_clean, width = 80)  # adjust width if needed
  )
  
  return(tbl)
   
}

```


```{r}
# There are 3 free  text questions 
comments1 <- feedback_text(data.feedback, 17)
comments2 <- feedback_text(data.feedback, 18)
comments3 <- feedback_text(data.feedback, 19)
```


**`r strwrap(comments1$title[1])`**

```{r}
kable(comments1$Comment, align = "l",
      escape = TRUE) %>%
    kable_styling(full_width = FALSE,
                  position = "left") %>%
    column_spec(1, width = "40em")
```



**`r strwrap(comments2$title[1])`**

```{r}

kable(comments2$Comment, align = "l",
      escape = TRUE) %>%
    kable_styling(full_width = FALSE,
                  position = "left") %>%
    column_spec(1, width = "40em")
```


**`r strwrap(comments3$title[1])`**

```{r}

kable(comments3$Comment, align = "l",
      escape = TRUE) %>%
    kable_styling(full_width = FALSE,
                  position = "left") %>%
    column_spec(1, width = "40em")
```






```{r}
 knitr::knit_exit()
```


