---
title: "Progress_Gender_Analysis"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
# Remember to disable png for Word export...
knitr::opts_chunk$set( message = FALSE, warning = FALSE, 
                       results =FALSE, echo = TRUE,
                       fig.width=7, fig.height=4, 
                       dev="png", 
                       dev.args=list(type="cairo"), dpi=96)


```


```{r packages}
library(forcats)
library(tidyverse)
library(ggplot2)
library(rstudioapi)
library(gmodels)
library(RColorBrewer)
library(xtable)
```



```{r}
# Sets the working directory to the file source folder
# This can throw an error if you run all chunks, if you rerun this chunk by itself though it will work.
## I think this is not needed,  when running notebooks thall paths are relaties to the notebook
# setwd(dirname(getActiveDocumentContext()$path))
# Make sure your markdown file is in the same folder as your data or modification will be needed
## I suggest we put the data in a "Data" folder
## Important note: Download the UTF-8.csv version 
raw_data <- read.csv('Data/progress.gender_analysis.csv', stringsAsFactors = TRUE)

```

# Cleaning
### Removing lecturers from the participants list

```{r}
## Remove less relevant observations 
#remove administrators

raw_data <- raw_data %>%
  rename( user = X)
  
raw_data <- filter(raw_data, !user %in% c("Christophe Bontemps","Ni Ni Thein", "Ju Ju Dawn", "Patrick Jonsson", 
                                      "sneha kaul", "Sharita Serraro",	"Akiyo Shibuya",  "Makoto Shimizu","
                                      Panpaka Supakalin", "Cecilia Tinonin"))
  

```



# Webinars replay

```{r}

# Webinar related plots 

# Careful here! Order of columns may vary depending on if they change name and/or if any modules are added/removed! 
header = c('Webinar1_Day1', 'Webinar1_Day2', 'Webinar2_Day1', 'Webinar2_Day2', 'Webinar3_Day1', 'Webinar3_Day2')
TOT_data <- raw_data %>% select(contains('ToT'))
names(TOT_data) = make.names(header)

# Processes the data into a format that ggplot can handle
processed_TOT_data <- TOT_data %>%
  pivot_longer(Webinar1_Day1:Webinar3_Day2, names_to = "Webinar", values_to = "Completed")
processed_TOT_data <- separate(
  processed_TOT_data, col = Webinar, into = c('Webinar','Day'),
  sep = "_")


TOT_plot <- ggplot(processed_TOT_data, aes(Day, fill = forcats::fct_rev(Completed)))+
  geom_bar(stat = 'count') +
  facet_wrap(~Webinar) + 
  theme_bw() + 
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_brewer(palette="Paired") +
  xlab('') +
  ylab('') +
  ggtitle('Number of views for webinar replay')

TOT_plot
```
```{r}
# Creates a crosstable for attendance in TOT webinars 
# Uses only data from day 1 to not double up the data, day 1 and day 2 have identical data.
CrossTable(processed_TOT_data$Webinar[processed_TOT_data$Day == 'Day1'],processed_TOT_data$Completed[processed_TOT_data$Day == 'Day1'],
           prop.t = F, prop.c = F, prop.chisq = F,
           dnn = c('',''))
```

# Modules completion 


> **Warning**: For each module, there are 3 elements recorded and corresponding to 3 elements on the LMS platform:

* The Articulate file (Interactive ppt)
* The pdf with the slides
* The pdf with questions and answers

 The activity of main interest here is whether there has been a view of the Articulate material, even if pdfs may have some interest too (some participants may substitute). 
 

 
```{r}
# Module related plot

# Extracts module columns that does not contain question and answers, but contains download version. 
Module_data <- raw_data %>% select(contains('Module.') & -contains('Questions.and.Answers') & contains('Download') & -contains('Annex'))

# Careful here! Order of columns may vary depending on if they change name and/or if any modules are added/removed! 
ModuleHeader = c('Module1', 'Module2', 'Module9', 'Module3', 'Module6', 'Module7',  'Module10')
names(Module_data) = make.names(ModuleHeader)

# Processes the data into a format that ggplot can handle
## Changing the order here to reflect the module sequences
processed_Module_data<- Module_data %>%
  pivot_longer(Module1:Module10 , names_to = "Module", values_to = "Completed") %>%
  mutate(Module = (fct_relevel(Module, rev(c("Module1", "Module2", "Module9",
                                         "Module3", "Module6", "Module7",
                                         "Module10")))))

Module_plot <- ggplot(processed_Module_data, aes(x = Module, fill = fct_rev(Completed))) +
  geom_bar() +
  theme_bw() + 
  theme(legend.title = element_blank()) +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab('') +
  ylab('') +
  scale_fill_brewer(palette="Paired") +
  ggtitle('Number of students that completed each module')+
  coord_flip()

Module_plot
```


```{r, results== "asis" }
# Creates a crosstable for completion of Modules
CrossTable(processed_Module_data$Module, processed_Module_data$Completed, prop.r = T, prop.t = F, prop.c = F, prop.chisq = F, dnn = c('',''))
```

# Individual participation
In this graphic, each line is a participant and each cell show the activity of the participant: It could be:

*  dark blue = Articulate view
*  light blue =  Pdf download only
*  white: No activity

**Ordering:** 
Horizontal: Sequence of Modules
Vertical: Participant should be ranked according to there overall participation for most active to inactive.
 


