---
title: "**Analyzing the Machine Learning e-Learning Course  <br> *(Using the Activity Log from Moodle)*  ** "
author: "Christophe Bontemps"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    df_print: kable
    toc: yes
    keep_tex: yes
    fig_width: 6.5
    fig_height: 4
    extra_dependencies: ["float"]
  html_document:
    df_print: paged
    toc: yes
    keep_md: yes
    code_folding: show
    fig_width: 6.5
    fig_height: 4
---


```{r Knitr_Global_Options, include=FALSE, cache=FALSE, echo=FALSE}
library(knitr)

# No code is shown here
knitr::opts_chunk$set(echo = FALSE)

# Other options used here 
opts_chunk$set(warning = FALSE, message = FALSE,
               fig.pos = "!H", fig.align = "center",
               autodep = TRUE, tidy = FALSE, cache = TRUE)

# In case of "weird" problem, uncomment the line below (cache issue)
opts_chunk$set(cache.rebuild=TRUE) 

# My colors:
SIAP.color <- "#0385a8"
```

`r if(knitr:::pandoc_to() == "latex") {paste("\\large")}` 


```{r libraries}

# Analysis
library(tidyverse)
library(stringr)
library(dplyr)
library(tidyr)
library(forcats)
library(lubridate)

# Nice presentation of results
library(Cairo)
library(papeR)
library(xtable)
library(kableExtra)
library(modelsummary)

# Graphics 
library(ggplot2)

library(plotly)
library(wesanderson)
```


```{r CourseParameters}
# Course specific parameters
CourseName <- "MLOS"     ##  "DTV20"
CourseNameLong <- "Machine Learning for Official Statistics and SDGs"
CourseStartDate <-"2021-11-08"
```


# Data 

```{r LoadData}
# Parse the data folder to find the latest files 

#### Logs File
#  Logs from https://siap-elearning.org/report/log/index.php?chooselog=1&showusers=0&showcourses=0&id=129&user=0&date=&modid=&modaction=&origin=&edulevel=-1&logreader=logstore_standard
# --> use Comma separated values
# Also https://siap-elearning.org/report/log/index.php?id=129

list.logs<- list.files(path="Data/",pattern="logs",full.names = TRUE,recursive = TRUE)
name_last_logs <- list.logs[which.max(file.mtime(list.logs))]
data.logs <- read.csv(name_last_logs)

# I have a strange pb with the name of the Time variable. fixing it quick and dirty mode !
data.logs <- data.logs %>% 
  rename(Time = ï..Time ) 

###  activity File:  Admin>Reports>Statistics> (select course and  period) activity completion 
# UTF-8.csv (= with comma separating)
# From https://siap-elearning.org/report/progress/index.php?course=129

list.act<- list.files(path="Data/",pattern="progress",full.names = TRUE,recursive = TRUE)
name_last_act <- list.act[which.max(file.mtime(list.act))]
data.act <- read.csv(name_last_act)

###  Grade File
list.grades<- list.files(path="Data/",pattern="Grades",full.names = TRUE,recursive = TRUE)
name_last_grades <- list.grades[which.max(file.mtime(list.grades))]
data.grades <- read.csv(name_last_grades)

FileDate <-as_date(file.mtime(name_last_logs))

```

We base our analysis on the files collected on `r FileDate` :

* `r name_last_logs` (Logs on the LMS)
* `r name_last_act `  (Learners activities)
* `r name_last_grades ` (latest grades compiled)


The Moodle platform allows the recording of many events during a course. Several data sets can then be downloaded (in *.csv* format) for an analysis of the activity of the learners. Each row of this log is an event and so all the events (course viewed, post, attempt to a test, , etc. ) are recorded, with a time stamp, in a single log file.  One field gathers the detail of each event as a text message. This field can be parsed and information on the user, the activity and the event can be extracted.

> For this course, we recorded **`r nrow(data.logs)`** events of different nature, that have to be cleaned.   

####  Cleaning log files

We have to perform several tasks before having some data to analyse. These task are generic to any course:

* Remove lecturers from the record

```{r cleaning}
## Remove less relevant observations 
#remove administrators

data.logs <- data.logs[!(data.logs$User.full.name=="Christophe Bontemps" |
                          data.logs$User.full.name=="Patrick Jonsson" |
                         data.logs$User.full.name=="Ni Ni Thein" |
                         data.logs$Component=="Recycle bin"),]
```

* Remove events recorded but not useful

```{r RemoveEvents}
#remove less relevant events

r <- unique(data.logs$Event.name)
# the events to remove

rem_events <- c("Tour ended", "Tour ended", "Group member added","Role assigned",
                "Course searched", "User list viewed", "User profile viewed",
                "Subscription created", 
                "User profile viewed", "User list viewed", "Course user report viewed",
                "Badge listing viewed", "User report viewed", "Course module instance list viewed",
                "Read tracking disabled", 
                "User enrolled in course", "Discussion deleted" , "Post deleted", 
                "Step shown", "Tour started", "Tour reset", "Quiz report viewed",
                "Subscription deleted", "User unenrolled from course", "Group member removed",
                "Role unassigned",  "Discussion subscription deleted", "Tag added to an item",
                "Grade deleted", tail(r, n=11))

# remove events
data.logs <- data.logs[!data.logs$Event.name %in% rem_events, ]

```

* Extract and identify activities from the log

> One important step is to extract and identify activities  from  the *Description* field and to affect identification numbers (IDs) to activities, Modules, types of activities, etc.  


```{r CourseLogData}
course_log <- data.logs

NbLearner <- as.numeric(count(unique((course_log %>%
              filter(!is.na(Event.name)) %>%
              select(User.full.name)))))
```

The course *`r CourseNameLong `* started on **`r CourseStartDate`**. On `r FileDate`, **`r paste0(NbLearner)`** different learners **visited**  the course.^[This number can be smaller than the number of people who registered since it only counts **visitors**. People who did not *visit* the LMS are thus not counted] Many different information can be extracted  from the log file: all the events, for all learners,  as well as the precise *time* of each event are recorderd. We can therefore gather information at the learner or activity level. 
 

```{r TimeID}
# Main course data frame 
course_log <- course_log  %>%
           mutate(Date = str_split(course_log$Time, ", " , simplify = TRUE)[,1],
                  HoursMin = str_split(course_log$Time, ", " , simplify = TRUE)[,2])

course_log <- course_log  %>%
          mutate(HoursMin = format(strptime(course_log$HoursMin, "%H:%M"), format = "%H:%M"),
          Date = as.Date(course_log$Date, "%d/%m/%y"))%>%
          filter(Date >= CourseStartDate) # rm before the the course started (13 Jan)


# Create day time range
# extract the hour and create time range. 
t <- course_log %>%
  select(HoursMin) %>%
  extract(HoursMin, 'Time_range', regex = "([\\d.]+)[^\\d.]", remove = FALSE) %>%
  mutate(Time_range = as.numeric(Time_range))

# a loop for time range
  for (i in list(t$Time_range)) {
  i = paste0(formatC(i, format="d",flag="0",width=2),":00", "-", formatC(i+1, format="d",flag="0",width=2), ":00")
  course_log$Time_range <- i
}

# unique(course_log$Time_range)

course_log <- course_log %>%
  mutate(DayID = group_indices(., Date))%>%
  mutate(TimeID = as.numeric(str_extract(course_log$Time_range, "([\\d.]+)")), 
         DayOfWeek = lubridate::wday(Date), 
         IsSunday  = as.factor(DayOfWeek ==7)) 

```


# Activities and events on the LMS

```{r ActivityData}

# Extract the activity names in order (hence the Header = FALSE above!)
# Here we need to have the name of the variables in the first row!!

data.act.temp<- read.csv(name_last_act, header = FALSE)
actname <- data.frame(t(data.act.temp[1,]))
names(actname) <- "Activity"
actname <-  actname %>%
  filter(!stringr::str_detect(Activity, "X") )%>%
  filter(!stringr::str_detect(Activity, "20") )%>%
  filter(stringr::str_detect(Activity, "") )%>%
  filter(!row_number() %in% c(1,2)) %>%
  mutate(ActNb = row_number())

## Attempt to a newer version (but names of activities are  with dots "General.Information"
# Extract the activity names in order (hence the Header = FALSE above!)
# actname <- data.frame(names(data.act), check.names=FALSE)
# names(actname) <- "Activity"
# 
# actname <-  actname %>%
#   filter(!stringr::str_detect(Activity, "X") )%>%
#   filter(!row_number() %in% c(1,2)) %>%
#   mutate(ActNb = row_number())
  
```

### List of all activities proposed on the course: 

```{r TableAct, echo=FALSE, results=TRUE}
ActivityTable <-  kable(actname, row.names = FALSE)
```

``````{r ModuleNb}
# Matching and adding columns
course_log <- course_log  %>%
  mutate(Actname = str_split(course_log$Event.context, ": ",
                             simplify = TRUE)[,2],
         Acttype = str_split(course_log$Event.context, ": ",
                             simplify = TRUE)[,1]         ) %>%
  left_join(actname, by = c("Actname" = "Activity"))

```

Some elements are specific to the course, such has the contain of each Module (weeks)

``````{r ModuleFilter}
### Define the Modules for each activity 
course_log <- course_log %>%
            mutate(ModuleID_2 = case_when(ActNb == 1 ~ -1,
                                          between(ActNb, 4, 11) ~ 0,
                                          between(ActNb, 12, 18) ~ 1,
                                          between(ActNb, 19, 27) ~ 2,
                                          between(ActNb, 28, 35) ~ 3,
                                          between(ActNb, 36, 50) ~ 4,
                                          between(ActNb, 51, 59) ~ 5,
                                          between(ActNb, 60, 68) ~ 6,
                                            )) %>%
   mutate(ActNb = formatC(ActNb, format="d",flag="0",width=2)) %>%
  filter(ActNb != "1")

```

```{r}
library(data.table)
Temp <- data.table(course_log %>% 
                     select(ModuleID_2, Actname) %>%
                     filter(ModuleID_2 >0) %>%
                     unique() %>%
                     mutate(ModuleID_2 =  paste("Module ", ModuleID_2))
                   )
tabl <-  Temp[, .N, keyby = ModuleID_2]
names(tabl) <- c("Module", "Nb of activities")
tabl
```

# Main outcomes of the course


After cleaning and refining the data, we have identified the  **`r length(unique(course_log$Actname))`**  different *activities* (resources such as videos, tutorials,  forums, articles, tests, polls,..) in the course and reported in this log. 

## Certified people

```{r}
# Step 1: Adding email address to course_log using data.act

StudentsNames <- data.act  %>%
  select(X, Email.address) %>%
  rename( User.full.name = X)

course_log <- left_join(course_log ,StudentsNames, by = c("User.full.name"))

# Step 2: Adding Sex and Country  to course_log using 
NameSex <- data.grades %>%
  mutate(TotalReal =  as.numeric(Course.total..Real.)) %>%
  select(Email.address, Sex, Country, TotalReal ) %>%
  mutate(Country = ifelse(Country =="", "Unknown", Country))

course_log <- left_join(course_log ,NameSex, by = c("Email.address"))

```


``````{r Certificates}
###  Certificates (here because removed afterwards)

CertifiedLearners <-  course_log %>%
    filter(stringr::str_detect(Actname, "certificate") ) %>%
  distinct(User.full.name, .keep_all=TRUE) %>% 
  select(User.full.name, Email.address,  Sex, Country, TotalReal)%>%
  unique()

NbCertificates <- nrow(CertifiedLearners)


```

There are **`r NbCertificates`** certified learners in this course out of  **`r paste0(NbLearner)`** (`r round(100*NbCertificates/NbLearner, 2)` %)

```{r}
DTCertified <- data.table(CertifiedLearners)
                   
CertifiedCountry<-  DTCertified[, .N, keyby = Country]
names(CertifiedCountry) <- c("Country", "Nb of Certificates")
CertifiedCountry[order(-`Nb of Certificates`)]
```
```{r}
CertifiedSex<-  DTCertified[, .N, keyby = Sex]
names(CertifiedSex) <- c("Sex", "Nb of Certificates")
CertifiedSex
```

### Attendance, Grades & Learners


```{r GradesTotal}

Grades <- data.grades %>%
  select(!(ID.number:Department)) %>%
  select(!(Position:Organization))%>%
  select(!contains("download"))%>%
  mutate_at(vars(matches("Quiz|Assign")),funs(as.numeric)) 


Grades <- Grades %>%
  mutate(
    GradeFinal = rowSums(dplyr::across(c(6:12)), na.rm = T)
  )
```





```{r GradesFile}

# We now have the full name in the grade file
# Grades <- Grades %>%
#   left_join(CertifiedLearners, by = c("Email.address"))
```


```{r GradesNames}
# Join to have the  certificate Owners
# Grades <- Grades %>%
#   left_join( CertificatesNames, by = c("Email.address"))

names(Grades)[6:12] <- c("Test1", "Test2", "Test3", "Test4", "Project", "Test5", "Test6")
  
```


We note that **`r Grades %>% filter(GradeFinal >=42*0.6) %>% nrow()`** have a grade greater than 70% of the maximum. 

The distribution of grades presented below excludes here the  *`r Grades%>% filter(GradeFinal ==0) %>% nrow()`* participants that did not participate in any of the tests (Grade =0).  


```{r Grades , fig.height=3}

Grades %>%
  filter(GradeFinal >0) %>%
 ggplot() +
 aes(x = GradeFinal) +
 geom_histogram(bins = 100L, fill = SIAP.color, color = "white") +
 coord_cartesian(xlim=c(0,66))+
 ggtitle("Grades distribution") +
 labs(x="Grades", y=" Nb of learners",
      caption = paste("(as of  ", FileDate,")"),
      subtitle = paste(Grades%>% filter(GradeFinal >=42) %>% nrow(),
                       "successful learners")
      )+
 annotate("rect", xmin = 42, xmax = 66,
                  ymin = 0, ymax = 40,
                  fill = SIAP.color , alpha = .2)+
   annotate("text", x = 50, y = 25,
          color= SIAP.color,
          label = "Success")+
 theme_minimal()

```


# Success by countries

## Learners

Since we have the information at the participant's level, we can have some statistics on the origin of the learners as well as performances by country. 

```{r}

Grades %>%
 filter(Country != "" | Country != "NA")%>%
 group_by(Country) %>%
 summarise(Learners = n_distinct(Email.address)) %>%
 ggplot() +
 aes( x=reorder(Country, Learners), y=  Learners) +
 geom_bar(aes(fill = Country),stat='identity', alpha = 0.3)+
geom_text(aes(label= Learners, color = Country), vjust= 0.3, size=3.5,)+
 scale_fill_hue() +
 ggtitle("Learners origin") +
 labs(y = "Nb of learners enrolled", 
      x = "Countries (Ordered by Nb of participants)",
      subtitle = paste("(date ", FileDate,")"))+
 coord_flip() +
 theme_minimal() +
 theme(legend.position = "none")


```

```{r densitySex, fig.height=4}
library(ggridges)
Grades %>%
 filter(Country != "" | Country != "NA")%>%
  filter(GradeFinal > 0) %>%
  group_by(Sex) %>%
  mutate(AvgGrade = mean(GradeFinal, na.rm =TRUE), 
         NbLearners = n_distinct(Email.address))  %>%
  ungroup() %>%
  filter(NbLearners >5) %>%
  ggplot() +
  aes(x = GradeFinal , y = reorder(Sex, AvgGrade) , fill = Sex) +
  xlim( c(0,65))+
  #geom_density_ridges(stat="binline", bins=20) +
  # geom_density_ridges( alpha = 0.3) +
  stat_density_ridges(quantile_lines = FALSE, quantiles = 2, 
                        jittered_points = TRUE,
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_shape = '|', point_size = 2, point_alpha = 0.3, 
                       alpha = 0.3
                      ) +
  #geom_jitter(color= SIAP.color, size=0.6, alpha=0.9) +
  ggtitle("Distribution of grades by Sex ") +
  labs(x="Final Grades", y=" Sex ", 
      subtitle = paste("(date ", FileDate,")")) +
    theme_ridges(grid = FALSE) +
  #theme_minimal()+
  theme(legend.position = "none")
 

```

```{r densityCountry, fig.height=4}
#library(ggridges)
Grades %>%
 filter(Country != "" | Country != "NA")%>%
  filter(GradeFinal > 0) %>%
  group_by(Country) %>%
  mutate(AvgGrade = mean(GradeFinal, na.rm =TRUE), 
         NbLearners = n_distinct(Email.address))  %>%
  ungroup() %>%
  filter(NbLearners >5) %>%
  ggplot() +
  aes(x = GradeFinal , y = reorder(Country, AvgGrade) , fill = Country) +
  xlim( c(0,65))+
  #geom_density_ridges(stat="binline", bins=20) +
  # geom_density_ridges( alpha = 0.3) +
  stat_density_ridges(quantile_lines = FALSE, quantiles = 2, 
                        jittered_points = TRUE,
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_shape = '|', point_size = 2, point_alpha = 0.3, 
                       alpha = 0.3
                      ) +
  #geom_jitter(color= SIAP.color, size=0.6, alpha=0.9) +
  ggtitle("Distribution of grades by countries ") +
  labs(x="Final Grades", y=" Countries (Ordered by Avg Grades) ", 
      subtitle = paste("Countries with more than 5 participants", "(date ", FileDate,")")) +
    theme_ridges(grid = FALSE) +
  #theme_minimal()+
  theme(legend.position = "none")
 

```





## Events {-}

When on the platform, the learners can interact with the activities in different ways. These interactions with the various types of activities can be regrouped in a typology of **`r length(unique(course_log$Event.name))-1`**  different type of events (as defined by Moodle)

```{r StatsEvents}
## Stat 
foo <-course_log %>%
  filter(
    str_detect(Event.name, "Quiz"))%>%
  mutate(
    Q = n_distinct(User.full.name) )

# Subset of posts CREATED on Forums (for counts below)
goo <-course_log %>%
  filter(
    str_detect(Event.name, "created"))%>%
  mutate(
    Q = n_distinct(User.full.name) )

# Subset of posts on Forums (for counts below)
hoo <-course_log %>%
  filter(
    str_detect(Event.context, "Forum"))%>%
  mutate(
    Q = n_distinct(ActNb) )

# Subset of Projects (for counts below)
poo <-course_log %>%
  filter(
    str_detect(Event.context, "Assignment") &
    str_detect(Description, "submitted") )%>%
  mutate(
     Q = n_distinct(User.full.name) )

```

Among the  **`r paste0(NbLearner)`** participants who visited the course, only  **`r max(foo$Q)`**  ( *`r round(100* max(foo$Q)/NbLearner, 1)`* %)   viewed or attempted a quiz at least once.  We can also note that **`r max(goo$Q)`**  ( *`r round(100* max(goo$Q)/NbLearner, 1)`* %)  participants posted at least one post in any of the **`r max(hoo$Q)`** forums proposed.   

We can also note that **`r max(poo$Q, na.rm=TRUE)`**  ( *`r round(100* max(poo$Q)/NbLearner, 1)`* %)  participants have submitted a file for the optional data-based project.

# Detailled analysis

## Learners views and completion by type of event

```{r TypeEvents}
course_log %>%
  filter(!is.na(Event.name)) %>%
  mutate(SpecificEvent = 
           ifelse(str_detect(Event.name, "Quiz"), "Test",
                  ifelse(str_detect(Event.name, "Discussion")|
                           str_detect(Event.name, "Post"), "Forum","Other"))) %>%
  group_by(Event.name, SpecificEvent) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 25) %>% 
  ggplot()+
  aes(x=reorder(Event.name, Learners), y=Learners, fill= SpecificEvent)+
  geom_bar(stat='identity')+
  labs(x="Events", y="Number of Learners", 
       subtitle = paste("The course has", length(unique(course_log$Event.name))-1,"different events (Final date ",
                        FileDate,")"))+
  ggtitle("Total number of learners per type of event")+
  scale_fill_manual("Type of Event",values=c("orange", "grey", SIAP.color)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
```



##  Events conducted by date and time of the day{-} 

We observe events over the whole period of the course and represent the activities by day. Thursdays and Wednesday seem to be the most active days. There is a clear decline of activity on Sundays, while the activity is very important on Thursdays, with the live lectures and webinars. 

```{r}

course_log %>%
  mutate(ParticularDays = ifelse(DayOfWeek ==7, "Sunday", 
                                 ifelse(DayOfWeek ==5 & DayID <30 | Date =="2021-12-16" , "Thursday", "Regular"))  ) %>%
  filter(!is.na(User.full.name)) %>%
  ggplot()+
  #aes(x=fct_infreq(Date))+
  aes(x = as.factor(DayID),  fill = ParticularDays)+
  geom_bar(color = "white" )+
  labs(x="Day since start", y="Number of events", 
       subtitle = paste("Nb of days", length(unique(course_log$Date)),"(Final date: ",
                        FileDate,")"))+
  ggtitle("Number of events recorded on the platform by date")+
  hrbrthemes::scale_fill_ft() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))

```

Since there is an important time difference between the teacher and the learners, it was important to have an idea of the learner's presence on the platform by hour.  The graphic below shows the maximum number of learners for different time periods of the day. 

```{r HourlyActivity, fig.height=3}
#Active time by Learners

course_log %>%
  filter(!is.na(Time_range)) %>%
  group_by(Time_range) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  ggplot()+
  aes(x=reorder(Time_range, Time_range), y=Learners, 
      fill = ifelse(Learners> 100, "High", "Low"))+
  geom_bar(stat='identity')+ 
  ggtitle("Number of Unique Visitors on the Platform by Hour")+
  labs(x="Time (JST)", y="Maximum Number of Learners", 
       subtitle = paste("Japan Time (Final date ", FileDate,")"))+
  scale_fill_manual("Activity",values=c("orange", SIAP.color)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8), 
        axis.text.x = element_text(angle = 60))
        
  # coord_flip()
  
```

    
### Learners preferred activities {-}

With no surprises, the learners' activities rank according to the modules order, with activities in module 1 on top and activities of modules 6 at the bottom. Some noticeable exceptions are the 6 quizzes, the data-based project and a homework,  that were more popular than other activities of their respective modules.    



```{r BarActivities, fig.height=8, fig.width=10, out.width = "80%"}

#final_date = as.Date(paste(FileDate), format = "%Y%m%d")

course_log %>%
  filter(!is.na(Event.context),
         Date <= FileDate) %>%
  mutate(ActID.lab = paste(ActNb,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarise(Learners = n_distinct(User.full.name),
            ModuleID = as.factor(unique(Actname))) %>%
  # mutate(rank = dense_rank(desc(Learners))) %>% 
  # filter(rank <= 30) %>% 
  mutate(ActID.lab = fct_reorder(ActID.lab, Learners, min)) %>%
ggplot() +
  aes(x = ActID.lab, fill = ModuleID, weight = Learners) +
  geom_bar() +
 # scale_fill_manual(values = c(wes_palette("Royal1")[1:2],wes_palette("Zissou1")) )+
  labs(x="Activities", y="Number of Learners")
  ggtitle("Activities accessed by number of Learners")+
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "none")
  
  

  # theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  #       plot.title = element_text(hjust = 0.5, size=12),
  #       panel.background = element_blank(), text = element_text(size=8),
  #       axis.line = element_line(colour = "black"),
  #       plot.subtitle = element_text(hjust = 0.5, size=8),
  #       axis.title.y = element_text(size = 8))+
 

#p
#ggplotly(p)

```

 
### Heatmap of the activities over time: 

This *heatmap* is an attempt to visualize the activities on the platform over time.  The coding is the following:

-  Horizontally:  time since beginning of course
-  Vertically:  activities (Module 1 at the bottom, module 6 at the top)
-  Heat = color:  Nb of views (Nb of Learners) for each activity 

```{r heatMap, fig.width=12, out.width = "90%"}
# course_log %>%
#   filter(!is.na(ActNb)) %>%
#   mutate(ActNb = formatC(ActNb, format="d",flag="0",width=2))


#Both Date and Date ID work. Date: the specific date since beginning; DayID: the first date = 1, and the second = 2, ...
library(colorspace)

course_log %>%
  filter(!is.na(ActNb)) %>%
  mutate(ActID.lab = paste(Actname,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab, Date) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  ggplot()+
  aes(x=Date, y= ActID.lab, fill=Learners)+
  geom_tile()+
  scale_fill_gradientn(colours=  diverge_hcl(4))+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(FileDate),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)


```

# Time and activities

```{r ActivityTime}
learners_Time <-  course_log %>%
  select(Email.address,  Actname, ActNb,Date, Time) %>%
  mutate(RealTime = lubridate::dmy_hm(Time)) %>%
  group_by(Email.address, Date) %>%
  arrange(RealTime) %>%
  mutate(RawDiff = RealTime - lag(RealTime))  %>%
  filter(RawDiff < 3600)%>%
  group_by(Email.address)%>%  
  summarise(TotalTime = sum(RawDiff, na.rm = TRUE), 
            NbAct = length(unique(Actname)), 
            NbDays = length(unique(Date))) %>%
  ungroup()
```


```{r LearnersFile}
Grades <- learners_Time %>%
  left_join(Grades, by = "Email.address") 

```


```{r}

Grades%>% 
  filter(Project >0) %>%
  nrow()
```


Over the `r nrow(Grades)` unique learners[^MyNote] registered for the course, only **`r Grades%>% filter(GradeFinal >0) %>% nrow()`** attempted  to at least one test and only **`r Grades%>% filter(NbDays > 6 ) %>% nrow()`** visited the LMS more than 6 times (the course is 6-weeks long).  

[^MyNote]: We removed SIAP's lecturers from the list  as well as some learners registered with different emails, we count here **unique** learners.  


We noticed that *some* learners (around `r round(Grades%>% filter(GradeFinal >50 & NbAct < 21) %>% nrow(), -1)` -  `r round(Grades%>% filter(GradeFinal >50 & NbAct < 25) %>% nrow(), -1)`) had very good grades in their tests ( >50) while showing a **very limited activity on the LMS** (less than a third of available).  

```{r}
Grades %>%
  filter(Country != "") %>%
 ggplot() +
 aes(x = NbAct, y = GradeFinal, color = Country) +
 geom_jitter( width = 0.5, height = 0.5, alpha = 0.6) +
 ggtitle("Test Scores vs Number of Activities Viewed") +
 labs(x="Nb of activities viewed", y=" Total Score (over 65)", 
      subtitle = paste(nrow(subset(unique(course_log[c("Actname", "Date")]),
                                   Date==FileDate)),"activities (date ", FileDate,
                       "). Each dot is a participant"))+
  annotate("rect", xmin= 0, xmax = 26, 
          ymin = 45, ymax = 65, 
          color= SIAP.color, alpha = 0.2) +
 # facet_wrap(vars(Country)) +
 scale_color_hue() +
 theme_minimal()
```


The time spent by learners on the platform is, of course, proportional to the number of activities viewed, with a greater heterogeneity for the most serious learners who viewed most of the activities.[^Time] 

[^Time]: We do not always observe when someone leaves the platform. The duration reported here may reflect *"shadow"* activities while the learner was doing something else.    


```{r}

p <- Grades %>%
 filter(!is.na(Country)) %>%
mutate(TotalTime = TotalTime/60) %>%
 ggplot() +
 aes(x = NbAct, y = TotalTime, colour = Country, toto = Email.address) +  
  # Toto is a trick to have names in plotly
 geom_jitter(aes(size=as.numeric(TotalTime)), width = 0.5, height = 0.5, alpha = 0.6) +
 ggtitle("Total Time Spent (estimated) vs Number of Activities Viewed") +
 labs(x="Nb of activities viewed", y=" Total time spent by learners (Duration, in min)", 
      subtitle = paste(nrow(subset(unique(course_log[c("Actname", "Date")]),
                                   Date==FileDate)),"activities (date ", FileDate,"). Each dot is a participant"))+
 geom_hline (aes(yintercept =  3*6*60), color = SIAP.color) +
 annotate("text", x = 12, y = 3*6*60 + 100,
          color= SIAP.color,
          label = "Course  requirement (3 hours/week)")+
# geom_vline (aes(xintercept =  median(TotalTime))) +
# facet_wrap(vars(Country)) +
 scale_color_hue() +
 theme_minimal()+
 theme(legend.position = "none")

p
#ggplotly(p)

```

## Grades {-}

We note that **`r Grades%>% filter(GradeFinal >=70) %>% nrow()`**, over the **`r Grades%>% filter(Project>0) %>% nrow() +6`**   who submitted a project (mandatory condition), succeeded with a grade above 70 (over 100). This is a rate of success of **`r round(100* (Grades%>% filter(GradeFinal >=70) %>% nrow()) / (Grades%>% filter(Project>0) %>% nrow() +6),1)`** %.

The distribution of grades presented below excludes here the  *`r Grades%>% filter(GradeFinal ==0) %>% nrow()`* participants that did not participate in any of the tests (Grade =0).  


```{r Grades1 , fig.height=3}

Grades %>%
  filter(GradeFinal >0) %>%
 ggplot() +
 aes(x = GradeFinal) +
 geom_histogram(bins = 100L, fill = SIAP.color, color = "white") +
 coord_cartesian(xlim=c(0,100))+
 ggtitle("Grades distribution") +
 labs(x="Grades", y=" Nb of learners", 
      subtitle = paste("(date ", FileDate,")"))+
 annotate("rect", xmin = 70, xmax = 101,
                  ymin = 0, ymax = 32,
                  fill = SIAP.color , alpha = .2)+
   annotate("text", x = 78, y = 25,
          color= SIAP.color,
          label = "Success")+
 theme_minimal()

```


> In date of `r as.Date(as.character(FileDate),format = "%Y%m%d")` ,   **`r NbCertificates`** participants have accessed the course certificate activity. 




```{r}
knitr::knit_exit()
```


# Leftovers


```{r, eval = FALSE}
#Learners event counts (top and bottom Learners)
course_log %>%
  filter(!is.na(User.full.name)) %>%
  count(User.full.name) %>%
  mutate(rank = dense_rank(desc(n))) %>% 
  filter(row_number() >= max(row_number()) - 5 | rank <= 5) %>%
  ggplot()+
  aes(x=reorder(User.full.name, -n), y=n, 
      fill=factor(ifelse(rank <= 5,"Top 5","Bottom 5"))) +
  geom_bar(stat='identity') +
  labs(x="Learners' ID", y="Number of events", fill="",
       subtitle = paste(NbLearner,"Learners (Final Date ", as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Learners event counts (top and bottom Learners)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```

### Activities accessed by number of Learners

> I changed the variable to have the labels and "see" which are the activities the most popular.  Could be good to the Module number too (1-6)!

```{r}
course_log %>%
  filter(!is.na(ActNb)) %>%
  mutate( ActID.lab = paste(ActNb,"-",Event.context, "-", ModuleID_2)) %>%
  group_by(ActID.lab) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  mutate(rank = dense_rank(desc(Learners))) %>% 
  filter(rank <= 40) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(length(unique(Actname))-1,"activities (Final Date ", as.Date(as.character(FileDate),format = "%Y%m%d"),")"))+
  ggtitle("Activities accessed by number of Learners (top 30 activities)")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
  
```




```{r}
course_log %>%
  filter(!is.na(ActNb),
         Date <= FileDate) %>%
  mutate( ActID.lab = paste(ActNb,"-",Event.context)) %>%
  group_by(ActID.lab) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  #mutate(rank = dense_rank(desc(Learners))) %>% 
  #filter(rank <= 30) %>% 
  ggplot()+
  aes(x=reorder(ActID.lab, Learners), y=Learners)+
  geom_bar(stat='identity')+
  labs(x="Activities", y="Number of Learners", 
       subtitle = paste(nrow(subset(unique(course_log[c("ActNb", "Date")]), Date==FileDate)),"activities (Date ", FileDate,")"))+
  ggtitle("Activities accessed by number of Learners")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=12),
        panel.background = element_blank(), text = element_text(size=8), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 8))+
  coord_flip()
```

 
 - Sort by the frequency of activities 
```{r, fig.width=12,fig.height=18}
#Both Date and Date ID work. Date: the specific date since beginning; DayID: the first date = 1, and the second = 2, ...
course_log %>%
  filter(!is.na(ActNb)) %>%
  mutate(ActID.lab = paste(ActNb,"-",Event.context, "-")) %>%
  group_by(ActID.lab, Date) %>%
  summarise(Learners = n_distinct(User.full.name)) %>% 
  ggplot()+
  aes(x=Date, y=fct_rev(fct_infreq(ActID.lab)), fill=Learners)+
  geom_tile()+
  labs(x="Date", y="Activities", 
       subtitle = paste("Final date ", as.Date(as.character(FileDate),format = "%Y%m%d")))+
  ggtitle("Heatmap of the activities")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        plot.title = element_text(hjust = 0.5, size=14),
        panel.background = element_blank(), text = element_text(size=10), 
        axis.line = element_line(colour = "black"), 
        plot.subtitle = element_text(hjust = 0.5, size=8),
        axis.title.y = element_text(size = 10))+
  coord_fixed(ratio = 0.5)

```



```{r }
# course_log <-  course_log %>%
#   group_by(User.full.name, Date, Actname) %>%
#   mutate( TimeperActivity = lubridate::as.duration(Time)) %>%
#   group_by(User.full.name, Date) %>%
#   mutate(TimeperDay = sum(TimeperActivity)) %>%
#   ungroup()
#  Still a problem in this computation since there may be hours btween two event...
```


```{r}

p <- Grades %>%
 filter(!is.na(Country)) %>%
mutate(TotalTime = TotalTime/60) %>%
 ggplot() +
 aes(x = NbAct, y = GradeFinal, colour = Country, toto = User.full.name) +
 geom_jitter(aes(size=as.numeric(TotalTime)), width = 0.5, height = 0.5, alpha = 0.6) +
# geom_vline (aes(xintercept =  median(TotalTime))) +
# facet_wrap(vars(Country)) +
 scale_color_hue() +
 theme_minimal()+
 theme(legend.position = "bottom")

p
#ggplotly(p)

```




# leftovers




```{r}

Grades%>%
 filter(Country != "" | Country != "NA")%>%
 group_by(Country)%>%
  summarise(Learners = n()) %>%
 ggplot() +
 aes( x=reorder(Country, Learners), y=  Learners) +
 geom_bar(aes(fill = Country), stat='identity', alpha = 0.3)+
 scale_fill_hue() +
 ggtitle("Learners origin") +
 labs(y = "Nb of learners enrolled", 
      x = "Countries (Ordered by Nb of participants)",
      caption = paste("(as of ", FileDate,")"))+
 coord_flip() +
 theme_minimal() +
 theme(legend.position = "none")


```

```{r density1, fig.height=4}
library(ggridges)
Grades %>%
 filter(Country != "" | Country != "NA")%>%
  filter(GradeFinal > 0) %>%
  group_by(Country) %>%
  mutate(AvgGrade = mean(GradeFinal, na.rm =TRUE), 
         NbLearners = n_distinct(User.full.name))  %>%
  ungroup() %>%
  filter(NbLearners >5) %>%
  ggplot() +
  aes(x = GradeFinal , y = reorder(Country, AvgGrade) , fill = Country) +
  xlim( c(0,65))+
  #geom_density_ridges(stat="binline", bins=20) +
  # geom_density_ridges( alpha = 0.3) +
  stat_density_ridges(quantile_lines = FALSE, quantiles = 2, 
                        jittered_points = TRUE,
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_shape = '|', point_size = 2, point_alpha = 0.3, 
                       alpha = 0.3
                      ) +
  #geom_jitter(color= SIAP.color, size=0.6, alpha=0.9) +
  ggtitle("Distribution of grades by countries ") +
  labs(x="Final Grades", y=" Countries (Ordered by Avg Grades) ", 
      subtitle = paste("Countries with more than 5 participants", "(date ", FileDate,")")) +
    theme_ridges(grid = FALSE) +
  #theme_minimal()+
  theme(legend.position = "none")
 

```

```{r}

Grades %>%
 filter(Country != "" | Country != "NA")%>%
 group_by(Country) %>%
 summarise(Learners = n_distinct(User.full.name)) %>%
 ggplot() +
 aes( x=reorder(Country, Learners), y=  Learners) +
 geom_bar(aes(fill = Country),stat='identity', alpha = 0.3)+
geom_text(aes(label= Learners, color = Country), vjust= 0.3, size=3.5,)+
 scale_fill_hue() +
 ggtitle("Learners origin") +
 labs(y = "Nb of learners enrolled", 
      x = "Countries (Ordered by Nb of participants)",
      subtitle = paste("(date ", FileDate,")"))+
 coord_flip() +
 theme_minimal() +
 theme(legend.position = "none")


```

```{r density2, fig.height=4}
library(ggridges)
Grades %>%
 filter(Country != "" | Country != "NA")%>%
  filter(GradeFinal > 0) %>%
  group_by(Country) %>%
  mutate(AvgGrade = mean(GradeFinal, na.rm =TRUE), 
         NbLearners = n_distinct(User.full.name))  %>%
  ungroup() %>%
  filter(NbLearners >5) %>%
  ggplot() +
  aes(x = GradeFinal , y = reorder(Country, AvgGrade) , fill = Country) +
  xlim( c(0,100))+
  #geom_density_ridges(stat="binline", bins=20) +
  # geom_density_ridges( alpha = 0.3) +
  stat_density_ridges(quantile_lines = FALSE, quantiles = 2, 
                        jittered_points = TRUE,
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_shape = '|', point_size = 2, point_alpha = 0.3, 
                       alpha = 0.3
                      ) +
  #geom_jitter(color= SIAP.color, size=0.6, alpha=0.9) +
  ggtitle("Distribution of grades by countries ") +
  labs(x="Final Grades", y=" Countries (Ordered by Avg Grades) ", 
      subtitle = paste("Countries with more than 5 participants", "(date ", FileDate,")")) +
    theme_ridges(grid = FALSE) +
  #theme_minimal()+
  theme(legend.position = "none")
 

```




